Visual Interrogation of Attention-Based Models: \\ Applications in Language Inference and Machine Comprehension

### 2018-05-28 EMNLP-demo-paper/NLPVis-demo-paper.tex
add figure
update intro

%\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here

@@

\newcommand\BibTeX{B{\sc ib}\TeX}
\newcommand\confname{EMNLP 2018}
\newcommand\conforg{SIGDAT}

@@

\author{Shusen Liu \\
  Lawrence Livermore National Laboratory  / 7000 East Ave, Livermore, CA 94550 \\
  {\tt email@domain} \\\And
  Tao Li \\
  University of Utah / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\}

>>>>

%\aclfinalcopy % Uncomment this line for the final submission

%\def\aclpaperid{***} %  Enter the acl Paper ID here

@@

\usepackage{graphicx}
\graphicspath{{figures/}{pictures/}{figs/}{./}} % where to search for the images

\newcommand\BibTeX{B{\sc ib}\TeX}
\newcommand\confname{EMNLP 2018}
%\newcommand\conforg{SIGDAT}

@@

\author{Shusen Liu \\
  Lawrence Livermore National Laboratory\\
  {\tt liu42@llnl.gov} \\\And
  Tao Li,  Zhimin Li,  Vivek Srikumar, Valerio Pascucci \\
  School of Computing, University of Utah\\
    {\tt {tao.li, zhimin.li, vivek, pacucci}@utah.edu}
}

### 2018-05-28 EMNLP-demo-paper/intro.tex
update intro

Neural networks have been successful in various natural language processing tasks,
where end-to-end training become a primary option \cite{Seo2016}.
As the design of neural networks evolve, there is a clear trend that more and more
parameters participate in training and prediction. While the strong expressivity
enhance model performance, the lack of interpretability presents challenge for analysis.
Without understanding the background meaning that features carry, visualization relies
on proper quantification analysis (cite). Such analysis is not easy to come up with,
and is tied to specific task (cite).

Recently attention networks become a widely-adopted setup (cite), partly because it yields
intermediate representations (e.g. alignment) that are not just beneficially expressive for performance,
but also intuitive to model. Indeed, the interpretability of attention networks introduce
a natural interface for analyzing the inside of neural networks. The wide popularity of attention networks
in recent NLP works necessitate a convenience framework for visualization and analyzing.

>>>>

Deep neural networks have been successfully applied to various natural language processing tasks,
where end-to-end training become a primary option \cite{Seo2016}.
As the design of neural networks evolve, there is a clear trend of increasing complexity of the model in term of architecture and parameters count. 
While the strong expressivity enhance model performance, the lack of interpretability presents challenge for analyzing and improving upon the existing models.
%Without understanding the background meaning that features carry, visualization relies
%on proper quantification analysis (cite). Such analysis is not easy to come up with,
%and is tied to specific task (cite).

Recently, attention networks have become a widely-adopted mechanism  \cite{VaswaniShazeerParmar2017, Parikh2016}, partly because it yields
intermediate representations (e.g. alignment) that are not just beneficially expressive for performance,
but also intuitive to model. Indeed, the interpretability of attention networks introduce
a natural interface for analyzing the inside of neural networks. The wide popularity of attention networks
in recent NLP works necessitate a convenience framework for visualization and analyzing.
